
% Main CV document. Individual sections are stored in the sections/ directory
\documentclass[a4paper,skipsamekey,11pt,english]{curve}

\PassOptionsToPackage{style=ieee,sorting=ydnt,uniquename=init,defernumbers=true}{biblatex}
\usepackage{settings}
\usepackage{multicol}

\DefineBibliographyStrings{english}{url={\textsc{url}}}

%% Only needed if you want a Publication List
% Bibliography file located in the bib/ directory
\addbibresource{bib/own-bib.bib}

\mynames{Beckwitt/David}
%% MAKE SURE THERE IS NO SPACE AFTER THE FINAL NAME IN YOUR \mynames LIST

% Change the fonts if you want
\ifxetexorluatex % If you're using XeLaTeX or LuaLaTeX
  \usepackage{fontspec}

  \usepackage[p,osf,swashQ]{cochineal}
  \usepackage[medium,bold]{cabin}
  \usepackage[varqu,varl,scale=0.9]{zi4}
\else % If you're using pdfLaTeX or latex
  \usepackage[T1]{fontenc}
  \usepackage[p,osf,swashQ]{cochineal}
  \usepackage{cabin}
  \usepackage[varqu,varl,scale=0.9]{zi4}
\fi

% Change the page margins if you want
% \geometry{left=1cm,right=1cm,top=1.5cm,bottom=1.5cm}

% Change the colours if you want
% \definecolor{SwishLineColour}{HTML}{00FFFF}
% \definecolor{MarkerColour}{HTML}{0000CC}

% Change the item prefix marker if you want
% \prefixmarker{$\diamond$}

%% Photo is only shown if "fullonly" is included
\includecomment{fullonly}
% \excludecomment{fullonly}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\leftheader{%
  {\LARGE\bfseries\sffamily David Beckwitt, Ph.D.}



  \makefield{\faEnvelope[regular]}{\href{mailto:David.Beckwitt@gmail.com}{\texttt{David.Beckwitt@gmail.com}}}
  \makefield{\faGithub}{\href{https://github.com/DVBeckwitt}{\texttt{@DVBeckwitt}}}
  \makefield{\faLinkedin}{\href{https://www.linkedin.com/in/beckwitt/}{\texttt{@Beckwitt}}}
  \makefield{\faOrcid}{\href{https://orcid.org/0009-0006-9122-1555}{\texttt{ORCID}}}
    { \\ Ph.D. candidate developing quantitative diffraction simulation tools and machine learning models to analyze crystalline disorder in 2D van der Waals materials; skilled in X-ray/neutron scattering, Chemical Vapor Deposition (CVD) thin-film growth, and computational modeling of structural defects.
}
}


\rightheader{~}
%\begin{fullonly}
% Profile picture stored in images/
%\photo[r]{images/photo}
%\photoscale{0.13}
%\end{fullonly}

\title{Curriculum Vitae}

\begin{document}
\makeheaders[c]

% Education
\begin{rubric}{Education}
  \entry*[May 2026 (expected)]%
    \textbf{University of Missouri, Columbia, MO --- Ph.D. in Physics}
    \par Dissertation: \emph{Investigating Disorder in van der Waals Thin Films}
    \par Advisor: Dr. Paul Miceli
  %
  \entry*[May 2022]%
    \textbf{University of Missouri, Columbia, MO --- M.S. in Physics}
  %
  \entry*[May 2020]{%
    \begin{tabular}[t]{@{}l@{}}
      \textbf{Missouri State University, Springfield, MO — B.S. in Physics}\\
      \hfill \textit{Minor: Mathematics}
    \end{tabular}%
  }
\end{rubric}

% Research Experience
\begin{rubric}{Research Experience}
  \entry*[2021 -- Present]%
    \textbf{Graduate Researcher,} University of Missouri; Advisor: Dr. Paul Miceli
    \begin{itemize}
      \item Developed a Python framework for quantitative modeling of area-detector GIWAXS measurements, implementing Reverse Monte Carlo methods to extract occupancies, anisotropic Debye--Waller factors, mosaicity, dimensionality, and laboratory geometry.
      \item Extended simulation tools to model diffuse intensities from stacking-fault distributions, enabling quantitative determination of fault densities.
      \item Grew phase-controlled PbI$_2$ thin films via CVD; validated simulations against experimental polytype fractions.
      \item Implemented convolutional neural networks trained on simulated GIWAXS images for automated, quantitative structural characterization of van der Waals thin-films.
    \end{itemize}

  \entry*[2019 -- 2020]%
    \textbf{Research Intern,} NASA Space Consortium
    \begin{itemize}
      \item Synthesized graphene thin films using pulsed laser deposition (PLD) and physical vapor deposition (PVD); characterized structural quality via Raman spectroscopy and electron microscopy.
    \end{itemize}

  \entry*[2017 -- 2020]%
    \textbf{Research Assistant,} Missouri State University; Advisors: Dr. Kartik Ghosh \& Dr. Saibal Mitra
    \begin{itemize}
      \item Designed, built, and operated a PLD system; characterized films via XRD, Raman spectroscopy, SEM/EDS, and force-sensitive profilometry.
    \end{itemize}

  \entry*[2019]%
    \textbf{Research \& Development Intern,} Dynatek Labs
    \begin{itemize}
      \item Developed software for biomedical testing and automated hardware systems.
    \end{itemize}
\end{rubric}

% Technical Skills
\begin{rubric}{Technical Skills}
  \begin{tabular}{@{}ll@{}}
    \textbf{Programming \& Data Analysis} & Python, Fortran, Git, MPI, Monte Carlo, Machine Learning (PyTorch) \\
    \textbf{Instrumentation \& Techniques} & X-ray/neutron scattering, CVD\\
    \textbf{Communication} & Technical writing, grant proposals, peer-review process\\
  \end{tabular}
\end{rubric}

% Publications
\makerubrichead{Research Publications}
\nocite{*}
\printbibliography[heading=subbibliography,title={Journal Articles},type=article]
\printbibliography[heading=subbibliography,title={Conference Proceedings},type=inproceedings]
\printbibliography[heading=subbibliography,title={In Review / In Preparation},keyword=inprep]

\pagebreak

% Teaching Experience
\begin{rubric}{Teaching Experience}
  \entry*[2018--2023]%
    \textbf{Instructor and Teaching Assistant}, University of Missouri and Missouri State University \RMPbadge\par
    \begin{itemize}
      \item Calculus-based Mechanics, Electricity \& Magnetism, and Introductory C++ Programming
    \end{itemize}

  \entry*[2021--Present]%
    \textbf{Academic Tutor}, Physics Courses, University of Missouri, Columbia, MO

  \entry*[2018--2021]%
    \textbf{ACT Prep Tutor}, Club Z!, Springfield, MO

  \entry*[2014--2020]%
    \textbf{Martial Arts Coach}, Dunham’s Martial Arts, Springfield, MO
\end{rubric}

% Leadership, Service & Outreach
\begin{rubric}{Leadership, Service \& Outreach}
  \subrubric{Professional Affiliations}
  \entry*[2017--2021] \textbf{Society of Physics Students}.
  \entry*[2019--Present] \textbf{American Physical Society}.
  \entry*[2020--Present] \textbf{Forum on the History and Philosophy of Physics}.
  \entry*[2022--Present] \textbf{Sigma Phi Sigma}.

  \subrubric{Outreach and Service}
  \entry*[2017--2020] \textbf{SPS High School Engagement}, Missouri State University.
  \entry*[2018--2019] \textbf{College of Natural and Applied Sciences Leadership Board}, Missouri State University.
  \entry*[2022]       \textbf{$\Sigma \Pi \Sigma$ Physics Congress – Presentation/Poster Judge}, Washington, DC.
  \entry*[2022--2023] \textbf{Coalition of Graduate Workers Diversity Officer}, University of Missouri.
  \entry*[2022--2023] \textbf{President, Physics and Astronomy Graduate Student Association}, University of Missouri.
  \entry*[2023--2024] \textbf{Vice-President, Physics and Astronomy Graduate Student Association}, University of Missouri.
  \entry*[2022--2024] \textbf{Director, PAGSA Mental Health Wellness Program}, University of Missouri.
  \entry*[2022--2024] \textbf{Research Outreach}, University of Missouri.

  \subrubric{Awards}
  \entry*[2021] \textbf{O.M. Stewart Scholarship}, University of Missouri.
  \entry*[2022] \textbf{Newell S. Gingrich Physics Scholarship}, University of Missouri.
  \entry*[2022] \textbf{Excellence in Student Leadership}, Graduate Professional Council, University of Missouri.
  \entry*[2022] \textbf{Excellence in Undergraduate Teaching}, University of Missouri.
  \entry*[2023] \textbf{Outstanding Student Research Presentation}, Neutron Scattering Society.
  \entry*[2023] \textbf{Excellence in Physics Fergason Scholarship}, University of Missouri.
  \entry*[2023] \textbf{Green Chalk Teaching Award}, University of Missouri.
  \entry*[2023] \textbf{Rangel-Boain Travel Award}, University of Missouri.
\end{rubric}
%\makerubric{sections/referee}

\end{document}

