\begin{rubric}{Research Experience}
    \entry*[2021 -- Present]%
        \textbf{Graduate Researcher,} University of Missouri; Advisor: Dr. Paul Miceli
        \begin{itemize}
            \item Created Fortran/Python code that fits area-detector data to extract occupancies, anisotropic Debye--Waller factors, in-plane mosaicity, percent dimensionality, and lab geometry (2025).
            \item Extended simulator to predict diffuse intensities from stacking-fault distributions, enabling quantitative fault density extraction.
            \item Grew phase-controlled PbI$_2$ by CVD; correlated polytype fraction with simulator outputs, achieving $\pm3\%$ agreement with experiment.
        \end{itemize}
    
    \entry*[2019 -- 2020]%
        \textbf{Research Intern,} NASA Space Consortium
        \begin{itemize}
            \item Synthesized and characterized graphene thin films via laser and PVD techniques.
        \end{itemize}
    
    \entry*[2017 -- 2020]%
        \textbf{Research Assistant,} Missouri State University; Advisors: Dr. Kartik Ghosh \& Dr. Saibal Mitra
        \begin{itemize}
            \item Designed and operated PLD system for thin film depositions.
            \item Characterized materials using XRD, AFM, SEM, and spectroscopy.
        \end{itemize}
    
    \entry*[2019]%
        \textbf{Research \& Development Intern,} Dynatek Labs
        \begin{itemize}
            \item Developed software for biomedical testing and automated hardware systems.
        \end{itemize}
\end{rubric}
