\begin{rubric}{Professional Activities and Contributions}

\subrubric{Professional Affiliations}
\entry*[2019--Present] \textbf{American Physical Society}.
\entry*[2020--Present] \textbf{Forum on the History and Philosophy of Physics}.
\entry*[2022--Present] \textbf{Sigma Phi Sigma}.
\entry*[2017--2021] \textbf{Society of Physics Students}.

\subrubric{Outreach and Service}
\entry*[2022] \textbf{$\Sigma \Pi \Sigma$ Physics Congress - Presentation/Poster Judging, Washington, DC}, Washington, DC.
\entry*[2022--Present] \textbf{CGW Diversity Officer}, University of Missouri.
\entry*[2022--Present] \textbf{President, Physics and Astronomy Graduate Student Association}, University of Missouri.
\entry*[2022-2024] \textbf{Director, PAGSA Mental Health Wellness Program, University of Missouri.}
\entry*[2017-2020] \textbf{SPS High School Engagement, Missouri State University}
\entry*[2018-2019] \textbf{CNAS Leadership Board, Missouri State University.}
\entry*[2022-2024] \textbf{ Research Outreach, University of Missouri.}

\subrubric{Awards}
\entry*[2023] \textbf{Outstanding Student Research Presentation}, Neutron Scattering Society.
\entry*[2021] \textbf{O.M. Stewart Scholarship, University of Missouri.}
\entry*[2022] \textbf{Newell S. Gingrich Physics Scholarship, University of Missouri}
\entry*[2022] \textbf{Excellence in Student Leadership}, Graduate Professional Council, University of Missouri.
\entry*[2022] \textbf{Excellence in Undergraduate Teaching}, University of Missouri.
\entry*[2023] \textbf{Excellence in Physics Fergason Scholarship, University of Missouri.}
\entry*[2023] \textbf{Green Chalk Teaching Award}, University of Missouri.
\entry*[2023] \textbf{Rangel-Boain Travel Award, University of Missouri}

\end{rubric}

