\begin{rubric}{Leadership, Service \& Outreach}

\subrubric{Outreach and Service}
\entry*[2023--2024]{\textbf{\href{https://pagsa.carrd.co}{Vice‑President, Physics and Astronomy Graduate Student Association (PAGSA)} – guided graduate student organization operations, University of Missouri.}}
\entry*[2022--2024]{\textbf{\href{https://pagsa.carrd.co}{Director, PAGSA Mental Health Wellness Program} – coordinated mental health initiatives, University of Missouri.}}
\entry*[2022--2024]{\textbf{\href{https://physics.missouri.edu/news/finding-community-physics-and-astronomy-student-organizations}{Research Outreach} – promoted physics research to the public, University of Missouri.}}
\entry*[2022--2023]{\textbf{\href{https://pagsa.carrd.co}{President, Physics and Astronomy Graduate Student Association (PAGSA)} – led graduate student advocacy and events, University of Missouri.}}
\entry*[2022--2023]{\textbf{\href{https://cgwmissouridotorg.wordpress.com/about/}{Coalition of Graduate Workers Diversity Officer} – advanced diversity and inclusion efforts, University of Missouri.}}
\entry*[2022]{\textbf{\href{https://students.aip.org/observer/reflections-on-the-2022-physics-congress}{Sigma Pi Sigma Physics Congress – Presentation/Poster Judge} – evaluated student research, Washington, DC.}}
\entry*[2018--2019]{\textbf{\href{https://blogs.missouristate.edu/cnas-newswatch/2022/04/13/trivia-night-brings-big-crowd-great-fun/}{College of Natural and Applied Sciences Leadership Board} – advised college initiatives, Missouri State University.}}
\entry*[2017--2020]{\textbf{\href{https://physics.missouristate.edu/_Files/2023_Newsletter_PAMS.pdf}{SPS High School Engagement} – mentored high school physics students, Missouri State University.}}

\subrubric{Awards}
\entry*[2023]{\textbf{\href{https://neutronscattering.org/prizes/nssa-outstanding-student-research/}{Outstanding Student Research Presentation} – honored for top research talk, Neutron Scattering Society of America.}}
\entry*[2023]{\textbf{\href{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Excellence in Physics Fergason Scholarship} – merit-based physics scholarship, University of Missouri.}}
\entry*[2023]{\textbf{\href{https://physics.missouri.edu/news/david-beckwitt-receives-green-chalk-award}{Green Chalk Teaching Award} – recognized for outstanding instruction, University of Missouri.}}
\entry*[2023]{\textbf{\href{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Rangel‑Boain Travel Award} – supported conference participation, University of Missouri.}}
\entry*[2022]{\textbf{\href{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Newell S. Gingrich Physics Scholarship} – awarded for academic excellence, University of Missouri.}}
\entry*[2022]{\textbf{\href{https://gpc.missouri.edu/resources-programs/awards/}{Excellence in Student Leadership} – acknowledged campus leadership, Graduate Professional Council, University of Missouri.}}
\entry*[2022]{\textbf{\href{https://physics.missouri.edu/sites/default/files/file-uploads/2021-03/physicsnewsletter2019-optimized_0.pdf}{Excellence in Undergraduate Teaching} – recognized teaching excellence, University of Missouri.}}
\entry*[2021]{\textbf{\href{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{O.M. Stewart Scholarship} – merit scholarship for physics students, University of Missouri.}}

\end{rubric}
